TADCompare: an R package for differential analysis and characterization of Topologically Associated Domains

### 2019-10-06 manuscript/manuscript.Rmd
Fix authors

# Coherence of Molecular Mechanisms in Genes Identified Through GWAS In Major Human Disease and Traits

Dozmorov, Mikhail G.^1+^ (mikhail.dozmorov@vcuhealth.org)  
Cresswell, Kellen G.^1+^ (cresswellkg@vcu.edu)  
Reimers, Mark^2^ (reimersm@msu.edu)  
Bacanu, Silviu-Alin^3^ (silviu-alin.bacanu@vcuhealth.org)  
Craver, Carl^4^ (ccraver@wustl.edu)  
Kendler, Kenneth S.^3^ (kenneth.kendler@vcuhealth.org)

^1^ - Department of Biostatistics, Virginia Commonwealth University   
^2^ - Neuroscience Program and Dept. Biomedical Engineering Michigan State  
^3^ - Virginia Institute for Psychiatric and Behavior Genetics and the Department of Psychiatry, Virginia Commonwealth University  
^4^ - Philosophy-Neuroscience-Psychology Program, Washington University in St. Louis  
^+^ - equal contribution

>>>>

# Coherence of Molecular Mechanisms <!--in Genes Identified Through GWAS -->In Major Human Disease and Traits

Dozmorov, Mikhail G.^1+^ (mikhail.dozmorov@vcuhealth.org)  
Cresswell, Kellen G.^1+^ (cresswellkg@vcu.edu)  
Bacanu, Silviu-Alin^2^ (silviu-alin.bacanu@vcuhealth.org)  
Craver, Carl^4^ (ccraver@wustl.edu)  
Reimers, Mark^3^ (reimersm@msu.edu)  
Kendler, Kenneth S.^2^ (kenneth.kendler@vcuhealth.org)

^1^ - Department of Biostatistics, Virginia Commonwealth University   
^2^ - Virginia Institute for Psychiatric and Behavior Genetics and the Department of Psychiatry, Virginia Commonwealth University  
^3^ - Neuroscience Program and Dept. Biomedical Engineering Michigan State  
^4^ - Philosophy-Neuroscience-Psychology Program, Washington University in St. Louis  
^+^ - equal contribution
